---
title: "Penguin_Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(palmerpenguins)
knitr::opts_chunk$set(echo = FALSE)
gradethis::gradethis_setup()
```


## Topic 1

1. **Select species and bill_length_mm [Code]**:

Write a code snippet to select the columns "species" and "bill_length_mm" from a data frame named "df".

```{r ex1, exercise = TRUE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df = penguins

### Write your Code Below



###

```

```{r ex1-solution, exercise.reveal_solution = FALSE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df %>% select(species, bill_length_mm)

```

```{r ex1-check}
grade_this({
  pass_if_equal(.solution_all, "Great")
  fail(hint = TRUE)
})
```

2. **Write a code use group_by and summarise [Code]**:

Write a code snippet that group the penguins by island and summarise by the mean of bill_length_mm ignoring empty values(use , na.rm = TRUE).


```{r ex2, exercise = TRUE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df = penguins

### Write your Code Below



###

```

```{r ex2-solution, exercise.reveal_solution = FALSE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df <- df %>%
  group_by(island) %>%
  summarise(mean(bill_length_mm, na.rm = TRUE))

print(df)

#

library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df %>%
  group_by(island) %>%
  summarise(mean(bill_length_mm, na.rm = TRUE))

print(df)



```

```{r ex2-check}
grade_this({
  pass_if_equal(.solution_all, "Great")
  fail(hint = TRUE)
})
```

3. **Create a column called 'body_mass_kg' [Code]**:

Write a code snippet that create a new column called 'body_mass_kg' by dividing the column 'body_mass_g' by 1000.

```{r ex3, exercise = TRUE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df = penguins

### Write your Code Below



###

```

```{r ex3-solution, exercise.reveal_solution = FALSE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df <- df %>%
  mutate(body_mass_kg = body_mass_g / 1000)

print(df)

#

library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df %>%
  mutate(body_mass_kg = body_mass_g / 1000)

print(df)



```

```{r ex3-check}
grade_this({
  pass_if_equal(.solution_all, "Great")
  fail(hint = TRUE)
})
```

4. **Write code that filter out [Code]**:

Write a code that filter out when bill_length_mm is larger than 30 mm AND bill_depth_mm is larger than 18 mm. 

```{r ex4, exercise = TRUE}
library(dplyr)
library(palmerpenguins)

df = penguins

### Write your Code Below



###

```

```{r ex4-solution, exercise.reveal_solution = FALSE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df %>%
  filter(bill_length_mm > 39, bill_depth_mm > 18)

#

library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df <- df %>%
  filter(bill_length_mm > 39, bill_depth_mm > 18)


```

```{r ex4-check}
grade_this({
  pass_if_equal(.solution_all, "Great")
  fail(hint = TRUE)
})
```

5. **Write code for flipper_length_mm [Code]**:

1. Select the code that group the penguins by species

2. Create a new column called summary_mean recording the mean using column flipper_length_mm with ignoring empty values ()


```{r ex5, exercise = TRUE}
library(dplyr)
library(palmerpenguins)

df = penguins

### Write your Code Below



###

```

```{r ex5-solution, exercise.reveal_solution = FALSE}
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df <- df %>%
  group_by(species) %>% 
  summarise(summary_mean = mean(flipper_length_mm, na.rm = TRUE))

#
library(gato365dsh2024)
library(dplyr)
library(palmerpenguins)

df %>%
  group_by(species) %>% 
  summarise(summary_mean = mean(flipper_length_mm, na.rm = TRUE))



```

```{r ex5-check}
grade_this({
  pass_if_equal(.solution_all, "Great")
  fail(hint = TRUE)
})
```

**MULTIPLE CHOICE**

```{r quiz}
quiz(
  question("If I want to select species type of penguin, what verb should I use?",
    answer("SELECT", correct = TRUE),
    answer("MUTATE"),
    answer("SUMMARISE"),
    answer("ARRANGE"),
    answer("FILTER")
  ),
  question("If I convert all of the weights of the penguin into a new column in the same data frame?",
    answer("SELECT"),
    answer("MUTATE", correct = TRUE),
    answer("SUMMARISE"),
    answer("ARRANGE"),
    answer("FILTER")
  ),
  question("If I want flipper_length_mm to be sorted in ascending order?",
    answer("SELECT"),
    answer("MUTATE"),
    answer("SUMMARISE"),
    answer("ARRANGE", correct = TRUE),
    answer("FILTER")
  ),
  question("If I want to find the mean for three groups with in my data?",
    answer("SELECT"),
    answer("MUTATE"),
    answer("SUMMARISE", correct = TRUE),
    answer("ARRANGE"),
    answer("FILTER")
  ),
  question("If I want to filter out penguins with bill_length_mm over 30 mm?",
    answer("SELECT"),
    answer("MUTATE"),
    answer("SUMMARISE"),
    answer("ARRANGE"),
    answer("FILTER", correct = TRUE)
  )
  )

```



